PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-05 paper/sec-results.tex
Top pair sect 3

\paragraph{Top-quark pair production.} We now consider

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
      differential top-quark pair measurement at a centre-of-mass energy of
      \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv}. Displayed are the distributions in the
      transverse momentum of the top quark $p_\mathrm{T}^\mathrm{t}$ (left), and in the invariant
      mass of the top-quark pair $m_{\mathrm{t}\bar{\mathrm{t}}}$ (right).}
    \label{fig:atlastop}
\end{figure}

>>>>

\paragraph{Top-quark pair production.} We now consider the top-pair differential
distributions measured by the ATLAS and CMS experiments at
\SI{7}{\tera\electronvolt}. In figure~\ref{fig:atlastop} we report the
distributions differential in the transverse momentum of the top quark,
$p_\mathrm{T}^\mathrm{t}$, and in the invariant mass of the top-quark pair,
$m_{\mathrm{t}\bar{\mathrm{t}}}$. Analogous plots for the distributions differential
in the rapidity of either the top quark or the top-quark pair are collected in
appendix~\ref{app:add_plots}. From figure~\ref{fig:atlastop}, we immediately
validate the \textsc{PineAPPL} result: its relative difference with respect to
the MC result is at most as large as $0.4\tcperthousand$, irrespective of the
accuracy of the theory, of the choice of scale and of the distribution
considered.

%-------------------------------------------------------------------------------
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
      differential top-quark pair measurement at a centre-of-mass energy of
      \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv}. Displayed are the distributions in the
      transverse momentum of the top quark $p_\mathrm{T}^\mathrm{t}$ (left), and in the invariant
      mass of the top-quark pair $m_{\mathrm{t}\bar{\mathrm{t}}}$ (right).}
    \label{fig:atlastop}
\end{figure}
%-------------------------------------------------------------------------------

The process is dominated by
